---
title: "HA 1"
author: "Xinrui Hu"
date: "2023-02-11"
output: pdf_document
---

Question 1
Calculate descriptive statistics of each of the variables.
```{r}
library("faraway")
summary(prostate)
```

Question 2
Create a scatter plot matrix for all the variables
```{r}
pairs(prostate)
```

Question 3
Calculate a (Pearson) correlation matrix for all the variables.
```{r}
cor(prostate)
```

Question 4
Show the same matrix again, but round the correlations (use three decimal places).
Which variable has the highest correlation with lcavol  (The variable represents the log(cancer volume in cm3)?
```{r}
round(cor(prostate),digits = 2)
# lpsa has the highest correlation with lcavol
```

Question 5
Show a scatter plot. Put lcavol in the y-axis and the variable you found in question 4 in the x-axis.

Include a regression line and label the axis.
```{r}
lg <- lm(lcavol ~ lpsa, data = prostate)
plot(prostate$lpsa, prostate$lcavol, 
     col = "blue", 
     xlab = "lpsa", ylab = "lcavol",
     abline(lg, col = "red"))

```

Question 6
Update the regression model you created for the regression line in question 5 by adding a second predictor: age.

Show the regression model output. What percentage of the variance of the outcome variables is explained by the two predictors?
```{r}
lg1 <- lm(lcavol ~ lpsa + age, data = prostate)
summary(lg1)
# 0.5498
```


Question 7
What is the Residual Standard Error of the model you created in Question 6?
```{r}
sqrt(deviance(lg1) / df.residual(lg1))
# 0.7991732
```

