---
title: "HA2"
author: "Xinrui Hu"
date: "2023-02-17"
output: pdf_document
---

1.1 Show descriptive statistics for each of the variables
What is the mean subjective taste score?
```{r}
library(faraway)
summary(cheddar)
# taste mean is 24.53
```

1.2 Show a histogram for each of the variables. Make sure to label the x-axis
```{r}
hist(cheddar$taste, xlab = "Taste")
hist(cheddar$Acetic, xlab = "Acetic")
hist(cheddar$H2S, xlab = "H2S")
hist(cheddar$Lactic, xlab = "Lactic")
```

1.3 Fit a regression model with taste as the response and no predictors.
What is the value of the intercept? What does it represent?
```{r}
Tnull <- lm(cheddar$taste ~ 1)
Tnull
# It represents the value of the mean of the taste
```

1.4 Fit a regression model with taste as the response and Lactic as the only predictor.
```{r}
summary(lm(taste ~ Lactic, cheddar))
# It is statistically significant at 5% level
```

1.5 Calculate the p-value of the model you created in Question 1.4 using the anova function.
```{r}
anova(lm(taste ~ Lactic, cheddar))
```

1.6 Fit a regression model with taste as the response and the three chemical contents as predictors. Identify the predictors that are statistically significant at the 5% level.
```{r}
mall <- lm(taste ~ Lactic + H2S + Acetic, cheddar)
summary(mall)
# It is statistically significant at 5% level
```

1.7 Use the anova function to recalculate the significance of the H2S variable as shown in the output of Question 1.6:
```{r}
model1 <- lm(taste ~ Lactic + Acetic, cheddar)
anova(model1,mall)
# p value is smaller than 5% so we can not frop the variable H2S
```

1.8 Test the hypothesis that the coefficients of Acetic and Lactic both equal 0 when H2S is included in the model. Should we reject this hypothesis?
```{r}
model2 <- lm(taste ~ H2S, cheddar)
anova(model2, mall)
# Fail to reject the null hypothesis since the p-value is greater than 5%
```

2.1 Convert sex into a factor and label and levels (male and female).
```{r}
teengamb$sex <- factor(teengamb$sex,
                        levels = c(0,1),
                        labels = c("male", "female"))
head(teengamb)
```

2.2 Fit a model with gamble as the response and income, verbal and sex as predictors. Which variables are statistically significant at the 5% level? 
```{r}
gmodel <- lm(gamble ~ income + verbal + sex, data = teengamb)
summary(gmodel)
# Income and sex are significant at the 5% level
# On average, the aggregate responses of female is 22.96 lower compared to male when we control for income and verbal
```

2.3 Use the confint function to produce 95% confidence intervals for the coefficients based on the same model. Can you deduce which coefficients are significant at the level of 5% based on the intervals?
```{r}
confint(gmodel, level = 0.95)
#  If the interval does not include zero, we can conclude that the corresponding coefficient is statistically significant at the 5% level.
```

