---
title: "HW3"
author: "Xinrui Hu"
date: "2023-02-25"
output: pdf_document
---

Question 1

Fit a regression model with the brozek variable (percent of body fat) as a response and the following five predictors: age, neck, abdom, forearm and wrist.
```{r}
library(faraway)
model <- lm(brozek ~  age + neck + abdom + forearm + wrist, fat)
summary(model)
# all the five variables are significant at  0.05 level
```

Question 2
Provide interpretation to the coefficient of each significant predictor
```{r}
#A one yrs increases in age is associated with average increases of 0.087 Percent of body fat using Brozek’s equation.
#A one cm increases in Neck circumference is associated with average decrease of 0.556 Percent of body fat using Brozek’s equation.
#A one cm increases in Abdomen circumference is associated with average increase of 0.721 Percent of body fat using Brozek’s equation.
#A one cm increases in Forearm circumference is associated with average increaase of 0.474 Percent of body fat using Brozek’s equation.
#A one cm increases in Wrist circumference is associated with average decrease of 2.05 Percent of body fat using Brozek’s equation.
```

Question 3
Compute the median values of the five predictors. Store the medians in a variable named x0 and show the values.
```{r}
x <- model.matrix(model)
(x0 <- apply(x,2,median))
```

Question 4
Construct a confidence interval of the mean response based on the median values that you stored in x0.
```{r}
predict(model, new = data.frame(t(x0)),interval = "confidence")
```

Question 5
Construct a prediction interval of future response value based on the median values that you stored in x0.
```{r}
predict(model, new = data.frame(t(x0)),interval = "prediction")
```

Question 6:
Which of the two intervals is wider?
The prediction interval is wider

Question 7:
Construct a confidence interval of the outcome variable for a person with the following characteristics:
Age: 50 years
Neck circumference: 42 cm
Abdomen circumference: 95 cm
Forearm circumference: 30cm
Wrist circumference: 17 cm
```{r}
x1 <- c("(Intercept)" = 1, age = 50, neck = 42, abdom = 95, forearm = 30, wrist = 17)
predict(model, new = data.frame(t(x1)),interval = "confidence")
```

