---
title: "HW5"
author: "Xinrui Hu"
date: "2023-03-10"
output: pdf_document
---

```{r}
library(faraway)
data = teengamb
```

Question 1: Create a regression with gamble as the outcome variable and sex, status, income, and verbal as predictors.

```{r}
model1 <- lm(gamble ~ sex + status + income + verbal, data)
summary(model1)
```

Question 2 Create a residuals vs. fitted plot. Do you think the variance is constant?

```{r}
plot(fitted(model1), residuals(model1), xlab = "Fitted",ylab = "Residuals", col = "blue")  
abline(h=0, col = "red") 
# No the variance is not constant
```

Question 3 Create a Quantile-Quantile plot and a histogram based on the standardized residuals. Does the distribution of residuals look normal?

```{r}
par (mfrow = c (1,2)) 
qqnorm(rstandard(model1), main = "")  
abline(0,1, col = "red")  
hist (rstandard(model1), main = "", xlab = "Standardized Residuals")
par (mfrow = c (1,1))
# The distribution of the residual is not normal
```

Question 4 Print all the standardized residuals. Are there any observations with standardized residuals greater than 3 or smaller than -3? If so, which ones? What are their standardized residuals?

```{r}
rstandard(model1)
# There are one standardized residual greater than 3 but no standardized residual smaller than -3. The standardized residual is 4.43
```

Question 5 Identify points with leverages that are at least two times the average leverage. Did you find any points? If so, which points did you find?

```{r}
hatv <- hatvalues(model1)
mean(hatv)
hatv [hatv > 2 * mean (hatv)]
# I found 4 points, the 31st, 33rd, 35th, and 42nd points.
```

Question 6 Detect outliers using studentized residuals. Use the Bonferroni correction. Which observations are detected, and what is their studentized residual?

```{r}
stud <- rstudent(model1)
stud[which.max(abs(stud))]
p <- 47 * 0.05
n <- 47
qt(1-.05 /(n*2),n-p-1)
which(abs(stud) > qt(1-.05/(n*2),n-p-1))
#Question 7
#Show the values of any outlier observation that you found in question 6 
#The 24th observation detected and  the studentized residual is 6.016
```

Question 8
Use Cook’s distances to search for influential points. Does any point have a Cook's distance above 0.5?
```{r}
cook <- cooks.distance(model1)
cook[which(cook > 0.5)]
# The 24th point has the cook's distance larger than 0.5
```

Question 9
Create a half normal plot. Which observation has the highest Cooks distance?
```{r}
countries <- row.names(data) 
halfnorm(cook,3, ylab = "Cook’s distances")
# The 24th point has the highest distance
```

