---
title: "hw6"
author: "Xinrui Hu"
date: "2023-03-18"
output: pdf_document
---


```{r}
library (faraway)
```

Question 1:
Fit a regression model with the brozek variable (percent of body fat) as a response and the following 13 predictors: age, weight, height, neck, chest, abdom, hip, thigh, knee, ankle, biceps, forearm, and wrist.
```{r}
model <- lm(brozek ~ age + weight + height + neck + chest + abdom + hip + thigh + knee + ankle + biceps + forearm + wrist, fat)
summary(model)
```

Question 2
Calculate pairwse correlations between the predictors (correlation matrix). Make sure to remove the outcome variable from the matrix.
```{r}
var1Removed <- fat[,-1]
corMatrix <- cor(var1Removed)
corMatrix <- round(corMatrix,2)
corMatrix
```

Question 3
Evaluate the collinearity by calculating the condition numbers of the eigenvalues. Are there any condition numbers above 30?
```{r}
x <- model.matrix(model)[,-1]
e <- eigen(t(x) %*% x)
e$val
sqrt(e$val[1] / e$val)
# There are condition value above 30
```

Question 4
Calculate the variance inflation factor for each predictor. Which inflation factors are greater than 10?
```{r}
rsq <- summary(lm(x[,1] ~ x[,-1]))$r.squared
rsq
1 / ( 1 - rsq)
require(faraway)
vif(x)
# weight and abdom inflation factor are greater than 10
```

Question 5
Fit a model with brozek as the response and age, weight, and height as predictors. Show the summary: 
```{r}
model1 <- lm(brozek ~ age + weight + height, fat)
summary(model1)
```

Question 6
Evaluate the collinearity by calculating the condition numbers of the eigenvalues. Are there any condition numbers above 30?
```{r}
x1<- model.matrix(model1)[,-1]
e1 <- eigen(t(x1) %*% x1)
e1$val
sqrt(e1$val[1] / e1$val)
# no condition number larger than 30
```

Question 7
Calculate the variance inflation factor for each predictor. Which inflation factors are greater than 10?
```{r}
rsq1 <- summary(lm(x[,1] ~ x[,-1]))$r.squared
rsq1
1 / ( 1 - rsq1)
require(faraway)
vif(x1)
# no factor greater than 10
```

