---
title: "hw7"
author: "Xinrui Hu"
date: "2023-04-04"
output: pdf_document
---

Question 1.1 Validate that the data contains 28 observations. Include
only observations with no missing values

```{r}
animalsDf <- read.csv("AnimalsStat.csv")
nrow(animalsDf [complete.cases(animalsDf ), ])
nrow (animalsDf)
```

Question 1.2 Show the first observations of the table

```{r}
head(animalsDf)
```

Question 1.3 Use the summary function to answer the following questions:
What is the average body mass? What is the average brain mass? Does the
data contain any animals with a body mass of 0 kg Does the data contain
any animals with a brain mass of 0 g Does the data contain any missing
values?

```{r}
summary(animalsDf)
# What is the average body mass? 4278.44kg
# What is the average brain mass? 574.52g
# Does the data contain any animals with a body mass of 0 kg ? No 
# Does the data contain any animals with a brain mass of 0 g ? No
# Does the data contain any missing values? No
```

Question 1.4 Which animal has the smallest and which has the largest
brain mass in the dataset?

```{r}
animalsDf[which.min(animalsDf$Brain),] # Mouse
animalsDf[which.max(animalsDf$Brain),] # African elephant
```

Question 1.5 Create a new variable for the brain-to-body mass ratio
(i.e., brain mass / body mass)

```{r}
library(tidyverse)
animalsDf <- animalsDf %>%  mutate(ratio = animalsDf$Brain / animalsDf$Body)
```

Question 1.6 Which animal has the smallest ratio, and which has the
largest?

```{r}
animalsDf[which.min(animalsDf$ratio),] # Brachiosaurus
animalsDf[which.max(animalsDf$ratio),] # Rhesus monkey
```

Question 1.7 Create the following four regressions: 1. Body mass as the
predictor and brain mass as the outcome 2. Log body mass as the
predictor and brain mass as the outcome 3. Body mass as the predictor
and log brain mass as the outcome 4. Log body mass as the predictor and
log brain mass as the outcome Show the summary for each model. Which one
has the largest R2?

```{r}
model1 <- lm(Brain ~ Body, data = animalsDf)
model2 <- lm(Brain ~ log(Body), data = animalsDf)
model3 <- lm(log(Brain) ~ Body, data = animalsDf)
model4 <- lm(log(Brain) ~ log(Body), data = animalsDf)
summary(model1)
summary(model2)
summary(model3)
# The model4 has the greatest R2
summary(model4)
```

Question 1.8 Create a scatter plot with a regression line and a
residuals vs fitted plot for the best regression.

```{r}
plot(model1, which=1, col = "blue")
```

Question 1.9 Based on the best model you found, Identify influential
points using a half-normal plot of the Cook's distances. Which three
animals have the largest distances?
```{r, warning=FALSE}
library(faraway)
cook <- cooks.distance(model1)
cook[which(cook > 0.5)]
Animals <- row.names(animalsDf) 
halfnorm(cook,3,labs = Animals , ylab = "Cook’s distances")
# Asian elephant, African elephant, Brachiosaurus have the largest distance
```

Question 1.10
Create a new data frame with the three observations removed
```{r}
df <- animalsDf[-c(7, 15, 26),]
```

Question 1.11
Fit a new model based on the new data frame (with the three points removed). Show again the type of plots you created for question 1.8
```{r}
lmod<- lm(Brain ~ Body, data = df)
plot(lmod, which=1, col = "blue")
```

Question 2.1
Fit a model with O3 as the outcome and temp, humidity, ibh as predictors. Which coefficients are significant at the 5% level?
```{r}
mod <- lm(O3 ~ temp + humidity + ibh, data = ozone)
summary(mod)
# all the predictors are significant at 5% level
```

Question 2.2
Fit the same model but add an interaction between temp and humidity.
Has the adjusted R2 increased compared to the previous model?
Is the interaction coefficient significant?
Is the temp variable significant?
Should we remove the temp variable while keeping the interaction?
```{r}
mod1 <- lm(O3 ~ temp + humidity + ibh + temp * humidity, data = ozone)
summary(mod1)
# R2 increased compare with the prior model, interaction model is significant, temp is not significant, we should remove it
```

Question 2.3
Create a residuals vs fitted plot. Do you detect any issues?
```{r}
plot(mod, which = 1, col = "blue")
# The plot is not linearly
```

Question 2.4
Create a Q-Q plot and histogram of the standardized residuals. Do you see any issues?
```{r}
par (mfrow = c (1,2)) 
qqnorm(rstandard(mod), main = "")  
abline(0,1, col = "red")  
hist (rstandard(mod), main = "", xlab = "Standardized Residuals")
par (mfrow = c (1,1))
```

Question 2.5
Use the Box-Cox method to find the optimal exponent for a power transformation of the outcome. What is the exponent that you found?
```{r, message= FALSE}
library(MASS)
require(MASS)
data(ozone, package = "faraway")
obj <- boxcox(mod, plotit = TRUE)
obj$x[which.max(obj$y)] # 0.26
```

Question 2.6
Create a new variable for the transformed outcome based on the maximum likelihood exponent and fit a new model with the same predictors (including the interaction term). Show the regression output.
```{r}
yTrans <- (ozone$O3)^(0.26) 
modTrans <- lm(yTrans ~ temp + humidity + ibh, data = ozone)
summary(modTrans)
```

Question 2.7
Create a residuals vs fitted plot for the new model. Do you see any difference?
```{r}
plot(modTrans, which = 1, col = "blue")
# The fitted line is more flat
```

Question 2.8
Create a Q-Q plot and histogram of the standardized residuals for the new model. Do you see any difference?
```{r}
par (mfrow = c (1,2)) 
qqnorm(rstandard(modTrans), main = "")  
abline(0,1, col = "red")  
hist (rstandard(modTrans), main = "", xlab = "Standardized Residuals")
par (mfrow = c (1,1))
```

