---
title: "final"
author: "Jinwoo Kim"
date: "2023-04-25"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm (list = ls()) # Clearing the memory

```

```{r,message=FALSE}
library(dplyr)
library(tidyverse)
library(knitr)
library(car)
options(scipen = 999)
df <- read.csv('newdf.csv')
df <- df %>% rename( "age" = "RIDAGEYR",
                     "gender" = "RIAGENDR",
                     "edu" = "DMDEDUC2",
                     "marry" = "DMDMARTL", 
                     "race" = "RIDRETH3", 
                     "height" = "WHD010", 
                     "weight" = "WHD020", 
                     "hi" = "HIQ011", 
                     "ogtt" = "LBXGLT") %>% na.omit(df$ogtt)
```

```{r}
# Deal with the abnormal value
df$height[df$height > 90] <- NA
df$weight[df$weight > 700] <- NA
df$hi[df$hi != 1] <- 2
# put the missing value with the mean of the data
df$weight[is.na(df$weight)] <- mean(df$weight, na.rm = TRUE)
df$height[is.na(df$height)] <- mean(df$height, na.rm = TRUE)
df$bmi <- signif((df$weight / (df$height^2))*703,4)
gender <- factor(df$gender, labels = c("Male", "Female"))
```

```{r}
summary(df)
```


```{r}
# Set up the plotting window with two plots side-by-side
par(mfrow = c(1, 2))
plot(density(df$height), main = "Height Density", xlab = "height")
plot(density(df$weight), main = "Weight Density", xlab = "Weight")
```

```{r}
par(mfrow = c(1, 2))
plot(density(df$bmi), main = "BMI Density", xlab = "BMI")
plot(density(df$age), main = "Age Density", xlab = "Age")
```
```{r}
par(mfrow = c(1, 2))
hist(df$height, main = "Height Hist", xlab = "height")
hist(df$weight, main = "Weight Hist", xlab = "Weight")
```

```{r}
par(mfrow = c(1, 2))
hist(df$bmi, main = "BMI Hist", xlab = "BMI")
hist(df$age, main = "Age Hist", xlab = "Age")
```






```{r}
par(mfrow = c(1, 2))
hist(df$ogtt, main = "Oral Test Hist", xlab = "Test")
plot(density(df$ogtt), main = "Oral Test Density", xlab = "Test")
```

```{r}
library ("gridExtra")
require(ggplot2)  
p1 <- ggplot(df, aes(hi, ogtt)) + geom_point() + stat_smooth(method="lm")
p2 <- ggplot(df, aes(age, ogtt)) + geom_point() + stat_smooth(method="lm")
p3 <- ggplot(df, aes(gender, ogtt)) + geom_point() +stat_smooth(method="lm")
p4 <- ggplot(df, aes(edu, ogtt)) + geom_point() + stat_smooth( method="lm")
p5 <- ggplot(df, aes(marry, ogtt)) + geom_point() + stat_smooth(method="lm")
p6 <- ggplot(df, aes(race, ogtt)) + geom_point() + stat_smooth(method="lm")
p7 <- ggplot(df, aes(bmi, ogtt)) + geom_point(position = position_jitter(width = .2,height=0)) 
grid.arrange(p1, p2, p3, p4, p5, p6, p7, nrow = 2)
```

```{r}
#Fitting a model 
lmod <- lm(ogtt ~ .-weight-height, df)
summary(lmod)
```

#PART1. Checking the equal variance assumption 
QQPLOT: check the nomarlity of errors assumtions with raw residuals 

```{r}
#Producing diagnistics plots:
par (mfrow = c(2,2))
plot (lmod)
par (mfrow = c(1,1))

```


#PART2: LEVERAGES 
Find large leverage values 

```{r}
#Identify points with leverages that are at least two times the average leverage.
hatv <- hatvalues(lmod)
#Any leverage that is at least twice as large as the average leverage is considered large.
hatv [hatv > 2 * mean (hatv)]
```
```{r}
#We can also make a histogram of the leverages and mark the threshold  value in red
hist (hatv, xlab = "Leverages", main = "")
abline(v = 2 * mean(hatv), col= "red")
```
#Answer: Points 8, 66, 111, ~ 2331, all have leverages twice as large as the avereage leverage.


```{r}
#
library("faraway")
individual <- row.names(df)
halfnorm(hatv, lab = individual, ylab ="Leverages" )
```

#As before, we can se that the leverages of 2295 and 1362 is very high. 

```{r}
#delete high leverage 
subdfleverage <- df[c(-8, -66, -111, -188, -418, -454, -626, -665, -711, -741, -891, -1026, -1049, -1076, -1077, -1232, -1300, -1362, -1368, -1465, -1477, -1488, -1506, -1553, -1572, -1595, -1597, -1664, -1677, -1720, -1731, -2024, -2058, -2074, -2121, -2177, -2291, -2295, -2331 ),]
lmod_leverage <- lm(ogtt ~ .-weight-height, subdfleverage)
summary(lmod_leverage)
```

```{r}
individual <- row.names(subdfleverage)
halfnorm(hatv, lab = individual, ylab ="Leverages" )
```

#Part 3: Outliers and Studentized Residuals

```{r}
lmod_leverage <- lm(ogtt ~ .-weight-height, subdfleverage)
summary(lmod_leverage)
```

```{r}
# Detect outliers using studentized residuals. Use the Bonferroni correction.
#Let us compute the studentized residuals for the savings data and pick out the largest one:

stud <- rstudent(lmod_leverage)
stud[which.max(abs(stud))]

```

```{r}
#In order to make a decision of whether to reject the null hypothesis that 19 is not an outlier. We need to calculate the Bonferroni critical value based on the t distribution:

p <- 5
n <- nrow (model.matrix(lmod_leverage))
qt(1-.05 /(n*2),n-p-1)
```
```{r}
which(abs(stud) > qt(1-.05/(n*2),n-p-1))

```
#observation 19, 221, ~1490 was detected as outliers 

```{r}
#delete outliers 
subdfoutliers <- subdfleverage[c(-19, -221, -488, -573, -583, -1205, -1242, -1423, -1556, -2108, -2222, -9, -139, -327, -392, -399, -813, -837, -960, -1046, -1399, -1468),]
lmod_outliers <- lm(ogtt ~ .-weight-height, subdfoutliers)
summary(lmod_outliers)
```





#Part 4: Influential Observations

```{r}
#Use Cook’s distances to search for influential points.
cook <- cooks.distance(lmod_outliers)
n <- nrow(subdfoutliers)
p <- 5
which(cook > qf(0.5, p, n-p))
```
#Answer: No cooks distance was above the threshold.


```{r}
library("faraway")
halfnorm(cook,3, ylab = "Cook's Distance")
```
```{r}
summary(lmod_outliers)
```


```{r}
param2Diff <- dfbeta(lmod_outliers)[,2]
plot(param2Diff,ylab = "Change in pop15 coef")
abline(h=0, col = "red")

```
```{r}
param2Diff [param2Diff > 0.4]
```
```{r}
param2Diff [param2Diff < -0.4]
```
```{r}
subdfdiff <- subdfoutliers[c(-886, -1941, -2100, -2237),]

lmod_diff <- lm(ogtt ~ .-weight-height, subdfdiff)
summary(lmod_diff)

```

#after delete influential obseravtion, now edu's significance has changed. 





```{r}
corMatrix <- cor(subdfdiff)
corMatrix <- round (corMatrix, 2)
corMatrix
```
```{r}
vif(lmod_diff)
```

```{r}
cook2 <- cooks.distance(lmod_diff)
halfnorm(cook2, 18, ylab = "Cook's Distance")

```

```{r}
plot(lmod_diff, which = 1, col = "blue")

```

```{r}
#Quantile-Quantile plot and a histogram based on the standardized residuals
par (mfrow = c (1,2)) 
qqnorm(rstandard(lmod_diff), main = "")  
abline(0,1, col = "red")  
hist (rstandard(lmod_diff), main = "", xlab = "Standardized Residuals")

```





```{r, warning=FALSE}
# AIC
require(leaps)
amod <- regsubsets(ogtt ~ .-weight-height, subdfdiff)
rs <- summary(amod)
rs$which
rs$rss
n <- nrow(subdfoutliers)
p <- 2:8
AIC <- n*log(rs$rss / n) + 2 * p
plot(AIC ~ I(p - 1), ylab = "AIC", xlab = "Number of Predictors", col = "blue")
# Fourth has the loest AIC 
modelaic <- lm(ogtt ~  hi+age + edu +bmi, subdfdiff)
```

```{r}
summary(modelaic)
```

```{r}
require(MASS)
obj <- boxcox(modelaic, plotit = TRUE)
```

```{r}
obj <- boxcox(modelaic, plotit = TRUE, lambda=seq(-0.8,0,by=0.1))

```

```{r}
mlLambda <- obj$x[which.max(obj$y)]
mlLambda
```

```{r}
yTrans <- df$ogtt^(mlLambda) # Transform the response
lmodTrans <- lm(yTrans ~ hi + age + edu + bmi,data = subdfdiff) # Fit a new regression

summary(lmodTrans)

```


```{r}
plot(lmodTrans, which = 1, col = "blue")
```


```{r}
par (mfrow = c (1,2)) 
qqnorm(rstandard(lmodTrans), main = "")  
abline(0,1, col = "red")  
hist (rstandard(lmodTrans), main = "", xlab = "Standardized Residuals")
```
```{r}
anova(lmod_diff,modelaic)
```

